Perturbation Theory in the Complex Plane: Exceptional Points and Where to Find Them

### 2020-12-05 Manuscript/EPAWTFT.tex
DONE

% ORBITAL OPTIMISATION EXCITED STATES
The present review has only considered the convergence of the MP series using the RHF or UHF 
reference orbitals.
However, numerous recent studies have shown that the use of orbitals optimised in the presence of the MP2 
correction\cite{Bozkaya_2011,Neese_2009,Lee_2018} or Kohn--Sham density-functional theory (DFT) orbitals 
can significantly improve the accuracy of the MP3 correction,\cite{Bertels_2019,Rettig_2020}
particularly in the presence of symmetry-breaking.
Beyond intuitive heuristics, it is not clear why these alternative orbitals provide such accurate results, 
and a detailed investigation of their MP energy function in the complex plane is therefore bound to provide
fascinating insights.
Furthermore, the convergence properties of the excited-state MP series using orbital-optimised higher energy 
HF solutions\cite{Gilbert_2008} remains entirely unexplored.\cite{Lee_2019,CarterFenk_2020}

% HUBBARD
Finally, the physical concepts and mathematical tools presented in this manuscript have been illustrated 
on the symmetric (or asymmetric in one occasion) Hubbard dimer at half-filling.
Although extremely simple, these illustrations highlight the incredible versatility of the Hubbard model
for understanding the subtle features of perturbation theory in the complex plane, alongisde other examples 
such as Kohn-Sham DFT, \cite{Carrascal_2015,Cohen_2016} linear-response theory,\cite{Carrascal_2018} 
many-body perturbation theory,\cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Hirata_2015,Tarantino_2017,Olevano_2019} 
ensemble DFT, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} thermal DFT,\cite{Smith_2016,Smith_2018} 
coupled cluster theory,\cite{Stein_2014,Henderson_2015,Shepherd_2016} and many more.
In particular, we have shown that the Hubbard dimer contains sufficient flexibility to describe 
the effects of symmetry breaking, the MP critical point, and resummation techniques, in contrast to the more 
minimalistic models considered previously.
We therefore propose that the Hubbard dimer provides the ideal arena for further developing our fundamental understanding
and applications of perturbation theory.

>>>>

% ORBITAL OPTIMISATION EXCITED STATES
The present review has only considered the convergence of the MP series using the RHF or UHF 
reference orbitals.
However, numerous recent studies have shown that the use of orbitals optimised in the presence of the MP2 
correction\cite{Bozkaya_2011,Neese_2009,Lee_2018} or Kohn--Sham density-functional theory (DFT) orbitals 
can significantly improve the accuracy of the MP3 correction,\cite{Bertels_2019,Rettig_2020}
particularly in the presence of symmetry-breaking.
Beyond intuitive heuristics, it is not clear why these alternative orbitals provide such accurate results, 
and a detailed investigation of their MP energy function in the complex plane is therefore bound to provide
fascinating insights.
Furthermore, the convergence properties of the excited-state MP series using orbital-optimised higher energy 
HF solutions\cite{Gilbert_2008,Barca_2014,Barca_2018a,Barca_2018b} remains entirely unexplored.\cite{Lee_2019,CarterFenk_2020}

% HUBBARD
Finally, the physical concepts and mathematical tools presented in this manuscript have been illustrated 
on the symmetric (or asymmetric in one occasion) Hubbard dimer at half-filling.
Although extremely simple, these illustrations highlight the incredible versatility of the Hubbard model
for understanding the subtle features of perturbation theory in the complex plane, alongisde other examples 
such as Kohn-Sham DFT, \cite{Carrascal_2015,Cohen_2016} linear-response theory,\cite{Carrascal_2018} 
many-body perturbation theory,\cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Hirata_2015,Tarantino_2017,Olevano_2019} 
ensemble DFT, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} thermal DFT,\cite{Smith_2016,Smith_2018} 
\titou{wave function methods},\cite{Stein_2014,Henderson_2015,Shepherd_2016} and many more.
In particular, we have shown that the Hubbard dimer contains sufficient flexibility to describe 
the effects of symmetry breaking, the MP critical point, and resummation techniques, in contrast to the more 
minimalistic models considered previously.
We therefore propose that the Hubbard dimer provides the ideal arena for further developing our fundamental understanding
and applications of perturbation theory.
